---
title: "README"
author: "Gonzalo Díaz"
date: "`r format(Sys.time(), '%d %B, %Y - %H:%M:%S')`"
output:
  md_document:
    variant: markdown_github
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# era5.aws R package
This R package (library) was created to handle ERA5 data obtained from Amazon (AWS) services.

## Clone the git repository
First, the repository containing the files needed to install the package must be cloned. From a terminal, run the following command:
```
git clone https://github.com/Gonzalo1985/era5.aws
```

## Pre-installed required packages
The era5.aws package needs to have the aws.s3 and devtools packages installed beforehand. From an R session run the following commands:
```{r, echo = TRUE, message = FALSE}
install.packages("aws.s3")
install.packages("devtools")
```
Then, open the "aws.s3" and "devtools" libraries:
```{r, echo = TRUE, message = FALSE}
library("aws.s3")
library("devtools")
```

## Package Installation
From the folder cloned with the files of the repository, execute the following command:
```{r, echo = TRUE, results = FALSE}
devtools::install()
```

Contact: Gonzalo M. Díaz (gonzalomartindiaz22@gmail.com)
