---
title: "README"
author: "Gonzalo Díaz"
date: "`r format(Sys.time(), '%d %B, %Y - %H:%M:%S')`"
output:
  md_document:
    variant: gfm
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# era5.aws R package
This R package (library) was created to handle ERA5 data (https://www.ecmwf.int/en/forecasts/datasets/reanalysis-datasets/era5) obtained from Amazon (AWS) services (https://registry.opendata.aws/ecmwf-era5/).

## Pre-installed required packages
The era5.aws package needs to have the "aws.s3", "terra" and "devtools" packages installed beforehand. From an R session run the following commands:
```{r, echo = TRUE, message = FALSE}
install.packages("aws.s3")
install.packages("terra")
install.packages("devtools")
```

## Package Installation
### Option 1
First, the repository containing the files needed to install the package must be cloned. From an OS terminal, run the following command:
```
$ git clone https://github.com/Gonzalo1985/era5.aws
```

From the folder cloned with the files of the repository, execute the following command from an R console:
```{r, echo = TRUE, results = FALSE}
devtools::install()
```

### Option 2
From an R console run the following command:
```{r, echo = TRUE, results = FALSE}
devtools::install_github("Gonzalo1985/era5.aws")
```

Contact: Gonzalo M. Díaz (gonzalomartindiaz22@gmail.com)
